\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex
addressed joe's changes

The frontend was implemented as a web app, using web technologies such as HTML,
CSS and JavaScript, with JavaScript being the vast majority. ECMAScript is the
standard that modern JavaScript follows.

Type-checking provided by Visual Studio Code and JSDoc made the growing code
complexity more manageable~\footnote{One helpful specification of the ECMAScript
standard in the way of programmer sanity is ``strict mode.'' By placing the
string \texttt{"use strict"} at the top of a JavaScript source file, errors will
be thrown in many cases where ordinary JavaScript would not complain. The
simplest example of this is the line \texttt{a = 1;} will not throw an error
ordinarily. In strict mode, you must at first explicitly declare the variable
with the \texttt{let}, \texttt{var} or \texttt{const} keyword before assigning
it, similar to Java or C++. We included the string at the beginning of every
source file except for class declarations, which are in strict mode by
default~\autocite[386]{ecmainternational2019}.} . Excluding Node.js modules, the
only external library we used for Editour was Leaflet, an open-source JavaScript
library for interactive maps~\autocite{leafletjs}. We did not use any framework
for developing frontends like Facebook's React or Google's Angular. Instead, all
of the complex UI interactions were handled by modifying the DOM directly with
JavaScript's built-in functionality. Furthermore, we did not use any advanced
frontend build tools such as Rollup, webpack or Parcel. For a JavaScript project
of this scope, this was the correct decision. Considering we had limited
knowledge of React or Angular, it was also faster to develop the UI in the way
we were used to from previous experience. But if we were to continue to develop
Editour, UI libraries and frontend build tools would be something to consider.

@@

Currently, anyone can clone the GitHub repository of Editour and deploy a
working version on a personal server. The source code for Editour is under an
open-source license. This allows anyone to expand the frontend and backend to
suit their needs. With additional hardware and by extending the current
implementation of both the frontend and backend, Editour could be used as the
groundwork to create an entire crowd-sourced walking tour platform, allowing
users to design tours for others to take.

In summary, we want to explore the idea of creating a community-driven audio
tour database that allows mobile users to take tours without the need to install
an app. The open-source code we wrote for Editour empowers us (or anyone else)
to develop and launch this platform in the future.

@@

ARuko, named after the Japanese word ``\begin{CJK}{UTF8}{min}歩こ\end{CJK}''
(\textit{aruko}), meaning ``let's walk,'' is the app we created to guide users
through an AR-enhanced tour. The app was built with Unity, which enabled to us
to use a single codebase for the iOS and Android versions of the apps.

@@

Over the course of the project, we had to develop multiple applications in
different languages. In total, we opened five different repositories: the blog,
the \LaTeX~source code for our paper, the Arduino code for the heart project,
and of course one for Editour and another for ARuko. These five repositories
span across multiple different markup and programming languages, including C\#,
C++, JavaScript, HTML, CSS (and the \LaTeX~markup language used to typeset this
paper.) This gave us a welcome amount of practice using Git for version control,
as well as GitHub's other features oriented around coordinating a team.

All three members of the team were contributing code and updating assets such as
graphics and sound. Code complexity grew quickly as more features were added
across the entire software stack. GitHub and Git enabled us to view the history
of the code and revert back to working versions when absolutely necessary. We
researched the proper methodology of using version control in a small team,
applying this methodology as best we could. This enabled us to work together
efficiently, track down bugs, undo mistakes, and sometimes review each other's
code for quality when time allowed.

@@

The Kanban technique stems from Toyota in the 1940s. Kanban means ``visual
signal'' or ``card'' in Japanese, which describes the core component of the
technique~\autocite{terry2019}. At Toyota, line-workers would move colored cards
to notify other teams that parts needed for assembly work were in short supply.
Now, Kanban boards are integral to Agile software development. Still, some teams
use physical Kanban boards, often using sticky notes and whiteboards.

The advantage of using a Kanban board is that each feature or bug that
is being worked on can be assigned directly to a collaborator on the project. It
is then that person's responsibility to work on those tasks and update the
status of those tasks on the board. We abandoned this when moving onto the main
project because we came to realize that this structure was not necessary---there
were only three members on the team, and we were almost always in the same room
when working on the project. For Editour, we tracked features and issues using
the Issues page instead, which is discussed in
Section~\ref{sec:editourFrontendTesting}.

@@

Once we deployed Editour to a server so that Atticus could begin to use it,
we changed the version to v1.0.0 to indicate the first release version. At this
point, it was important that the master branch remain as stable as possible.
Because of this, we created a ``dev'' branch where we could test experimental
features to improve the experience and functionality of Editour. Maintaining a
stable and experimental branch reduced the risks involved with continuing to
iterate on the software's features post-release.

@@

Throughout our stay at Ritsumeikan, we also had the opportunity to work closely
with other Ritsumeikan students to create build a project that involved the
integration of hardware and software. With the help of students and professors
alike, we were able to produce an educational physical model of a heart
controlled by an Arduino microcomputer. Noma gave us tremendous assistance with
hardware. He taught us how to properly use the tools around the lab, and
purchased mechanical and electrical components we would need to complete our
task. Amano Sensei was always available to answer questions related to biology,
and helped us understand the mathematical model we would need to implement to
drive the physical model with software. We worked on this project every
Wednesday, completing the final model during the last week of our stay.
% TODO get the full name of Amano Sensei

@@

We were presented with a set of equations that defined the mathematical model of
the heart we would be using to drive our physical model. Along with the
differential equations, we were also given an analogous circuit model that could
also be described by the same equations. The circuit and the equations can be
seen in Figure~\ref{fig:referenceModel}. We were also provided with source code
for an implementation of this model. We would still need to modify this code to
calculate the output variables we would need to properly operate the physical
model, and integrate the model into the main loop of the Arduino source code
with the appropriate timing.

@@

With Noma Sensei as our guide, we visited ``Den Den Town'' in Osaka in order to
gather supplies we would need in order to construct the heart. One of the most
important purchases of this trip was a two-meter long strip of Adafruit NeoPixel
light emitting diodes (LEDs). The design of this reel of LEDs enabled us to cut
the strip at specific points to create shorter strips. Each LED on the strip
individually addressable, allowing us to set the color of any LED along the
strip. This perfectly suited our needs for representing blood flow.

@@

Not only can the GUI communicate with the Arduino; the Arduino can relay
information about the state of the model back to the GUI. The length of blue bar
on the left of Figure~\ref{fig:heartGui} corresponds to $f_{v}$ in the model,
while the blue bar on the right corresponds to $f_{1}$. On the physical model,
these values correspond to the rate of animation of both LED strips. The size of
the circle between the blue bars represents $V_{LV}$, the volume of the left
ventricle. Due to limitations about the accuracy with which we could control the
pump, the volume of the balloon does perfectly reflect the true value of
$V_{LV}$ in the model. By contrast, the radius of the graphic on-screen can be
set to be exactly proportional to the value of $V_{LV}$.

>>>>

The frontend was implemented as a web application, using web technologies such
as HTML, CSS and JavaScript, with JavaScript being the vast majority of the
code. Type-checking provided by Visual Studio Code and JSDoc made the growing
code complexity more manageable.\footnote{One helpful specification of the
ECMAScript standard in the way of programmer sanity is ``strict mode.'' By
placing the string \texttt{"use strict"} at the top of a JavaScript source file,
errors will be thrown in many cases where ordinary JavaScript would not
complain. The simplest example of this is the line \texttt{a = 1;} will not
throw an error ordinarily. In strict mode, you must at first explicitly declare
the variable with the \texttt{let}, \texttt{var}, or \texttt{const} keyword
before assigning it, similar to Java or C++. We included the string at the
beginning of every source file except for class declarations, which are in
strict mode by default~\autocite[386]{ecmainternational2019}.} Excluding Node.js
modules, the only external library we used for Editour was Leaflet, which is
``an open-source JavaScript library for mobile-friendly interactive maps''
according to the official Leaflet website~\autocite{leafletjs}. We did not use
any framework for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel. For
a JavaScript project of this scope, this was the correct decision. Considering
we had limited knowledge of React or Angular, it was also faster to develop the
UI in the way we were used to from previous experience. But if we were to
continue to develop Editour, UI libraries and frontend build tools would be
something to consider.

@@

Currently, anyone can clone the GitHub repository of Editour and deploy a
working version on a personal server. The source code for Editour is under a
free license. This allows anyone to expand the frontend and backend to suit
their needs. With additional hardware and by extending the current
implementation of both the frontend and backend, Editour could be used as the
groundwork to create an entire crowd-sourced walking tour platform, allowing
users to design tours for others to take.

In summary, we want to explore the idea of creating a community-driven audio
tour database that allows mobile users to take tours without the need to install
an app. The free code we wrote for Editour empowers us (or anyone else)
to develop and launch this platform in the future.

@@

% TODO let's triple check the name in Japanese even makes sense
ARuko, named after the Japanese word ``\begin{CJK}{UTF8}{min}歩こ\end{CJK}''
(\textit{aruko}), meaning ``let's walk,'' is the app we created to guide users
through an AR-enhanced tour. The app was built with Unity, which enabled to us
to use a single codebase for the iOS and Android versions of the apps.

@@

Over the course of the project, we had to develop multiple applications in
different languages. In total, we created five different repositories: the blog,
the \LaTeX~source code for our paper, the Arduino code for the heart project
(see Appendix~\ref{sec:ritsumeikanHeartProject}) and of course one for Editour
and another for ARuko. These five repositories span across multiple different
markup and programming languages, including C\#, C++, JavaScript, HTML, CSS (and
the \LaTeX~used to typeset this paper). This gave us a welcome amount of
practice using Git for version control, as well as GitHub's other features
oriented around coordinating a team.

All three members of the team were contributing code and updating assets such as
graphics and sound. Code complexity grew quickly as more features were added
across the entire software stack. GitHub and Git enabled us to view the history
of the code and revert back to working versions when absolutely necessary. We
researched the proper methodology of using version control in a small team,
applying this methodology as best we could. This enabled us to work together
efficiently, track down bugs, undo mistakes, and review each other's code for
quality when time allowed.

@@

The Kanban technique stems from Toyota in the 1940s. Kanban means ``visual
signal'' or ``card'' in Japanese, which describes the core component of the
technique~\autocite{terry2019}. At Toyota, line-workers would move colored cards
to notify other teams that parts needed for assembly work were in short supply.
Now, Kanban boards are integral to Agile software development. Some teams still
use physical Kanban boards, often using sticky notes and whiteboards.

The advantage of using a Kanban board is that each feature or bug that
is being worked on can be assigned directly to a collaborator on the project. It
is then that person's responsibility to work on those tasks and update the
status of those tasks on the board. We abandoned this when moving onto the main
project because we came to realize that this structure was not necessary---there
were only three members on the team, and we were almost always in the same room
when working on the project. For Editour, we tracked features and issues using
the ``Issues'' page instead, which is discussed in
Section~\ref{sec:editourFrontendTesting}.

@@

In order to clearly indicate new versions of the software, we use ``Semantic
Versioning'' which is a scheme for version numbers created by Tom
Preston-Werner, cofounder of GitHub~\autocite{prestonwerner}. In this scheme,
the full version number consists of three integers separated by periods---in
other words, in the form \texttt{major.minor.patch}. The major version number is
incremented when an incompatible change is made. In our case, an incompatible
change for Editour would entail changing the format of the metadata file used to
construct a tour such that the frontend could not interpret older tour files.
The exception to this rule is major version 0, where the product is not
considered stable and incompatible changes can be made at any time. When Editour
was in this phase of development, we changed the format of the metadata; this
would have broken previous versions but this was allowed. The minor version
number is incremented when functionality is added but remains backwards
compatible with previous versions. An example of this is the ``transcript''
field we added to the metadata. The frontend was still able to load tours made
before this additional information was added to the metadata JSON. We added many
other features throughout the development process without breaking existing
functionality. The patch version number is for simple bug-fixes that also do not
break compatibility. This number gets incremented the most frequently in
practice.

Once we deployed Editour to a server so that Atticus could begin to use it, we
changed the version to 1.0.0 to indicate the first release version. At this
point, we were committed to not making any backwards-incompatible change. Since
Atticus would be interacting with Editour after the release of 1.0.0, it was
important that the master branch remain as stable as possible. Because of this,
we created a ``dev'' branch where we could test experimental features to improve
the experience and functionality of Editour. Maintaining a stable branch along
with a separate experimental branch reduced the risks involved with continuing
to iterate on the software's features post-release.

@@

Throughout our stay at Ritsumeikan, we also had the opportunity to work closely
with other Ritsumeikan students to create build a project that involved the
integration of hardware and software. With the help of students and professors
alike, we were able to produce an educational physical model of a heart
controlled by an Arduino microcomputer. Noma Sensei gave us tremendous
assistance with hardware. He taught us how to properly use the tools around the
lab, and purchased mechanical and electrical components we would need to
complete our task. Amano Sensei was always available to answer questions related
to biology, and helped us understand the mathematical model we would need to
implement to drive the physical model with software. We worked on this project
every Wednesday, completing the final model during the last week of our stay.
% TODO get the full name of Amano Sensei

@@

We were presented with a set of equations that defined the mathematical model of
the heart we would be using to drive our physical model. Along with the
differential equations, we were also given an analogous circuit model that could
also be described by the same equations. The circuit and the equations can be
seen in Figure~\ref{fig:referenceModel}. We were also provided with source code
for an implementation of this model in C. We would still need to modify this
code to calculate the output variables we would need to properly operate the
physical model, and integrate the model into the main loop of the Arduino source
code with the appropriate timing.

@@

With Noma Sensei as our guide, we visited ``Den-Den Town'' or Nipponbashi in
Osaka in order to gather supplies we would need in order to construct the heart.
One of the most important purchases of this trip was a two-meter long strip of
Adafruit NeoPixel light emitting diodes (LEDs). The design of this reel of LEDs
enabled us to cut the strip at specific points to create shorter strips. Each
LED on the strip individually addressable, allowing us to set the color of any
LED along the strip. This perfectly suited our needs for representing blood
flow.

@@

Not only can the GUI communicate with the Arduino; the Arduino can also relay
information about the state of the model back to the GUI. The length of blue bar
on the left of Figure~\ref{fig:heartGui} corresponds to $f_{v}$ in the model,
while the blue bar on the right corresponds to $f_{1}$. On the physical model,
these values correspond to the rate of animation of both LED strips. The size of
the circle between the blue bars represents $V_{LV}$, the volume of the left
ventricle. Due to limitations about the accuracy with which we could control the
pump, the volume of the balloon does perfectly reflect the true value of
$V_{LV}$ in the model. By contrast, the radius of the graphic on-screen can be
set to be exactly proportional to the value of $V_{LV}$.
